intro

### 2022-08-15 06_Paper/ER-ED/ERED_Stage2/method.Rmd
corrected package

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))

stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
```

>>>>

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Trials", "negative.xlsx")), range = cellranger::cell_cols("A:D"))

stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Trials", "neutral.xlsx")), range = cellranger::cell_rows(1:21))
```
